Inferring ecological interactions

### 2016-11-30 index.Rmd
add spreadsheet and google docs links

[Dominique Gravel](), [Tim Poisot](), [Kevin Cazelles,]() [Ben Weinstein](benweinstein.weebly.com), [Ignacio Bartomeus](),Ignacio Morales Castilla, David Beauchesne, Mickaël Hedde, Mathilde Besson, Steve Vissault, Guillaume Blanchet

@@

@@

>>>>

[Dominique Gravel](), [Tim Poisot](), [Kevin Cazelles,](http://kevincazelles.fr/) [Ben Weinstein](benweinstein.weebly.com), [Ignacio Bartomeus](),Ignacio Morales Castilla, David Beauchesne, Mickaël Hedde, Mathilde Besson, [Steve Vissault](http://steveviss.github.io/), Guillaume Blanchet

@@

### Website

@@

### Google doc:

[Here](https://docs.google.com/document/d/1x1YHzF-vZXbrQUIF97TNqyIJ6bXyaEiFjMsi18nJDag)

### Spreadsheet :

[Here](https://docs.google.com/spreadsheets/d/1Nps6BsDrkWMbvLa_lsgc5MT8RBtTeFX6hWlUjsRlkO0/edit?ts=583f2190#gid=1879087403)
